---
title: "Analysis of UCR data"
output: html_notebook
---

--------------
Load Libraries
--------------

```{r}
# xtable: print tables into LaTeX
# zeallot: unpack returned objects from functions
pacman::p_load(pacman, tsibble, "readxl", dplyr, haven, markdown, readr, stringr, tidyverse, xtable, did, gridExtra,zeallot)
```

------------------------------------
Functions that load and prepare data
------------------------------------

### load_data
```{r}
load_data <- function(filename) {
  # This function loads the data and creates a yearmonth column
  # usage: df_cs <- load_data("event_study_data_1994-2016_michigan")
  df_cs <- read_dta(paste("../Data/Processed/", filename, ".dta", sep=""))
  # change the format of dates to datetime
  df_cs$date <- as.Date(df_cs$date)
  df_cs$nibrs_start_date <- as.Date(df_cs$nibrs_start_date)
  df_cs$nibrs_start_yearmonth <- yearmonth(df_cs$nibrs_start_date)
  df_cs$yearmonth <- yearmonth(df_cs$date)
  return(df_cs)
}
```

### remove_missing
Fn: Remove ORIs that do not report consistently
```{r}
remove_missing <- function(df_cs) {
  # This function removes reporting agencies that don't report consistently over time
  # ex. df_cs <- remove_missing(df_cs)
  data_months = length(unique(df_cs$date))
  df_cs <- df_cs %>%
    group_by(ori9) %>%
    filter(n() == data_months)  
  return(df_cs)
}
```

### remove_high_discrepency
Fn: Remove ORIs that have zero crime rate for some of the months, but high crime rate for other ones.
```{r}
remove_high_discrepency <- function(df, crime_column, freq) {
  # This function removes ORIs if they have zero crime rate for some of the months, but large crime rate for other ones
  # ex. df_cs <- remove_high_discrepency(df_cs, crime_rate, freq = 'monthly')
  if (freq=='monthly'){
      df <- df %>% 
        group_by(ori9) %>% 
        filter(min(crime_rate) != 0 | max(crime_column) <= 500)
  } else if (freq=='yearly'){
      df <- df %>%
        group_by(ori9) %>%
        filter(min(crime_rate) != 0 | max(crime_column) <= 5000)
  }
  return(df)
}
```

Import yearmonth variable
```{r}
# import the file that matches a yearmonth variable to an integer to meet the requirement of the algorithm
df_yearmonth <- read_excel("../Data/yearmonth_numeric.xlsx")
```

### data_preparation
Fn: Prepare data for event study analysis
```{r}
# prepare data for event study analysis
data_preparation <- function(df_cs, fals=NULL) {
  # This function prepares the data for event study analysis
  # It creates an integer value for the yearmonth variable
  # It also factorize the ID variable and the state names
  # ex: df_cs_numeric <- data_preparation(df_cs).
  # ex for falsification test: df_cs_numeric <- data_preparation(df_cs, fals)
  # merge with df_yearmonth to introduce an integer value for yearmonth variable
  df_cs_numeric <- left_join(df_cs, df_yearmonth, by = c("date" = "yearmonth")) 
  df_cs_numeric <- df_cs_numeric %>%  rename(date_numeric = numeric)
  # merge on nibrs_start_date to introduce an integer value for yearmonth variable
  df_cs_numeric <- left_join(df_cs_numeric, df_yearmonth, by = c("nibrs_start_date" = "yearmonth"))
  df_cs_numeric <- df_cs_numeric %>% rename(nibrs_numeric = numeric)
  # falsification
  if(!is.null(fals)) {
    df_cs_numeric$nibrs_numeric <- df_cs_numeric$nibrs_numeric + 12
  }
  df_cs_numeric$nibrs_numeric[is.na(df_cs_numeric$nibrs_numeric)] <- 0
  # create variable to factorize the ID variable
  df_cs_numeric$ori9_factors <- factor(df_cs_numeric$ori9)
  df_cs_numeric$ori9_factors <- as.integer(df_cs_numeric$ori9_factors)
  # factorize the state names
  df_cs_numeric$state_fac <- factor(df_cs_numeric$state_name)
  return(df_cs_numeric)
}
```

### replace_neg
Fn: Replace negative values with the mean of the ori
```{r}
replace_neg <- function(df, crime_type){
  # The number of crimes is reported as negative for some years for some reporting agencies. These values are replaced with the mean values for the reporting agency.
  # ex. replace_neg(df, total_crime)
  # enquo takes the arguments and returns the value as a quosure.
  crime_type = enquo(crime_type)
  # inside of mutate, we ask it to unquote (using !!) so that it gets evaluated
  df <- df %>%
    group_by(ori9) %>%
    mutate(!!crime_type := ifelse(!!crime_type < 0,
                                mean(!!crime_type, na.rm=TRUE),
                                !!crime_type)) 
  return(df)
}
```

### data_cleaning
```{r}
data_cleaning <- function(data_file, year=FALSE) {
  # This function cleans the data, including dropping data from DC, removing agencies that did not report crime consistently throughout the data period, preparing the data for event study analysis, and grouping the data by the year (optional)
  # removes data from DC, oris that have missing data, and oris that report zero for some months, but large numbers for other months
  # ex. data_cleaning("event_study_data_1994-2016_robust", TRUE)
  df <- load_data(data_file)
  df <- df[df$state_name != "District of Columbia" & df$state_name != "", ]
  df <- remove_missing(df)
  df <- data_preparation(df)
  if (year==TRUE) {
    df <- group_by_year(df)
    df <- remove_high_discrepency(df, crime_column="actual_all_crimes", "year") 
  }
  else {
    df <- remove_high_discrepency(df, crime_column="actual_all_crimes", "date") 
  }
    # Use total crime column as criterion for removing ORIs with zero values because it is more reliable as a criterion. The other crime categories could have very small observations.
    return(df)
}
```



### event_study_plot
Fn: Event study plot
```{r}
# function for event study plots
# freq = {"monthly", "annual"}
# ex. event_study_plot(es, xlimits = c(-174, 180), xbreaks = seq(-174, 180, by = 24),                         ylimits = c(-500, 500), ybreaks = seq(-500, 500, by = 250),                            es_mms_1994_2016, freq = annual, title="(a) Real Data")
event_study_plot <- function(es, xlimits = NULL, xbreaks = NULL, 
                             ylimits = NULL, ybreaks = NULL, filename, freq,
                             title = NULL) {

  if (freq == "monthly") {
    xgap = 24
  } 
  else if (freq == "annual") {
    xgap = 4
  }
  g <- ggdid(es, xgap = xgap)
  if ((!is.null(xbreaks) || !is.null(xlimits)) && 
      (!is.null(ybreaks) || !is.null(ylimits))) {
    g <- g + scale_x_continuous(limits = xlimits, breaks = xbreaks) +
      scale_y_continuous(limits = ylimits, breaks = ybreaks)
  }
  else if (!is.null(xbreaks) || !is.null(xlimits)) {
    g <- g + scale_x_continuous(limits = xlimits, breaks = xbreaks)
  }
  else if (!is.null(ybreaks) || !is.null(ylimits)){
    g <- g + scale_y_continuous(limits = ylimits, breaks = ybreaks)
  }
  g <- g + ggtitle(title) # add the title of the plot
  g <- g + xlab("Years") + ylab("Change in crime count difference") # add the axis labels
  g <- g + labs(caption = "Vertical bars are 95% confidence intervals.")
  g <- g + theme(aspect.ratio = .6)
  ggsave(path = "../Figures/", device = "png", 
         filename = paste(filename, ".png", sep=""), 
         plot = g, width = 8.75, height = 5.40, dpi = 100)
  return(g)
}
```

### calculate_effect_size
Fn: Save effect size data
```{r}
# ex. df_es_1994_2016_mi <- calculate_effect_size(es, "crime", "1994_2016_mi", "annual")
calculate_effect_size <- function(es, crime, file_info, freq) {
  # freq = {"annual", "monthly"}
  if (freq == "monthly") {
    # calculate effect size
    df_es <- data.frame(es$egt, es$att.egt, es$se.egt)
    # make variable - years before / after treatment
    df_es$year <- df_es$es.egt %/% 12 + 1
    # average by the year
    df_temp <- df_es %>%
                group_by(year) %>%
                summarise_at(vars(es.att.egt), list(name = mean))
    # the above needs work to transform the se
  } else if (freq == "annual") {
    # put event study data into a dataframe
    df_temp <- data.frame(es$egt, es$att.egt, es$se.egt)
    df_temp <- df_temp %>%
      rename(year = es.egt,
             mean = es.att.egt,
             se = es.se.egt)
  }
  # record effect size
  csv_name <- paste("es_year_", crime, "_", file_info, sep = "")
  csv_path <- paste("../Data/Processed/", csv_name, ".csv", sep="")
  write.csv(df_temp, file = csv_path, row.names = FALSE)
  return(df_temp)
}
```

### make_latex_table
Fn: Make LaTeX table
```{r}
make_latex_table <- function(main_dataframe, robustness_dataframe = NULL,crime_name,crime_abbr) {
  # The function prints out a latex table
  # Ex: make_latex_table(df_es, df_es_rc,crime_type="crime",crime_abbr="c")
  tbl_title <- paste("Change in",crime_name)
  # if the function is given both dataframes
  if (!is.null(robustness_dataframe)) {
    df_tbl <- merge(main_dataframe, robustness_dataframe, by = "year")
    df_tbl <- subset(df_tbl, year > 0 & year < 6)
    # rename columns
    names(df_tbl) <- c('Years After Switch', 'Change (FBI UCR)','SE (FBI UCR)', 'Change (Alt. UCR)', 'SE (Alt. UCR)')
    print(xtable(df_tbl, digits = c(0, 0, 2, 2, 2, 2),caption = tbl_title),caption.placement='top', include.rownames = FALSE,file=paste("../Tables/esna_", crime_abbr, ".txt", sep=""))
  }
  # if the function is given only one dataframe
  else {
    df_tbl <- main_dataframe[(main_dataframe$year < 6) & (main_dataframe$year > 0),]
    # rename columns
    names(df_tbl) <- c('Years After Switch', 'Change', 'SE')
    print(xtable(df_tbl, digits = c(0, 0, 2, 2),caption = tbl_title),caption.placement='top', include.rownames = FALSE,file=paste("../Tables/esn_",crime_abbr,".txt",sep=""))
  }
}
```

### did_agg
```{r}
did_agg <- function(crime_name,crime_abbr, data_type){
  # this function aggregates the output into a did format, make it into a table, and store it as a .csv file
  # it is invoked in the function `post_processing`
  # ex. did_agg(crime_name,crime_abbr, data_type)
  # did type aggregation
  att <- aggte(out, type="simple", na.rm = FALSE) # if there are NA values, they will be removed, and not aggregated to create NA in the aggregate
  # make table for did
  dfatt <- data.frame(crime_name=numeric())
  dfatt[1,] <- att$overall.att
  dfatt[2,] <- att$overall.se
  colnames(dfatt) <- crime_name
  # store the table
  csv_name <- paste("did_year_", crime_abbr, "_1994_2016_", data_type, sep = "")
  csv_path <- paste("../Data/Processed/", csv_name, ".csv", sep="")
  write.csv(dfatt, file = csv_path, row.names = FALSE)
  return(dfatt)
}
```


### post_processing
```{r}
post_processing <- function(data_type,crime_abbr,crime_name,title,freq,alt=FALSE){
  # this function conducts post processing after regression
  # ex. post_processing(data_type="na",crime_abbr="c",crime_name="crime",title="Event study of total crime (Alternative UCR)","annual")
  # event study type aggregation
  es <- aggte(out, type = "dynamic", na.rm = TRUE)
  summary(es)
  # event study plot
  p <- event_study_plot(es, filename = paste("es_",data_type,"_",crime_abbr,"_1994_2016",sep=""), freq = "annual",
                 title = title, xbreaks = seq(-20, 16, by = 4))
  # calculate effect size for synthetic data
  df <- calculate_effect_size(es=es, crime=crime_name, paste("1994_2016",data_type,sep="_"), freq = "annual")
  # if we are looking at the alternative UCR, we include the original UCR in the LaTeX table for comparison. Otherwise, we only include data from the original UCR
  if (alt==TRUE) {
    dff <- read_csv(paste("../Data/Processed/es_year_",crime_name,"_1994_2016_n.csv",sep=""))
    # make latex table for event study
    make_latex_table(main_dataframe=dff, robustness_dataframe=df,crime_name,crime_abbr)
  }
  else {
    make_latex_table(main_dataframe=df,crime_name=crime_name,crime_abbr=crime_abbr)
  }
  # make did table
  did_agg(crime_name=crime_name, crime_abbr=crime_abbr,data_type=data_type)
  # return the event study plot
  return(p)
}
```

Test code for `did_comb`
```{r}
dftemp <- read_csv(paste("../Data/Processed/did_year_","c","_1994_2016_n.csv",sep=""), show_col_types = FALSE)
dftemp2 <- read_csv(paste("../Data/Processed/did_year_","m","_1994_2016_n.csv",sep=""), show_col_types = FALSE)
cbind(dftemp,dftemp2)
```

### did_comb
```{r}
did_comb <- function(data_source){
  # this function combines did results from separate tables
  # see --did-- subsections in each regression section for details
  dftemp <- read_csv(paste("../Data/Processed/did_year_","c","_1994_2016_", data_source, ".csv",sep=""), show_col_types = FALSE)
  did_crime_names <- list("m","p","r","a","aa","b","t")
  # this function combines the did regression results across different types of crime
  for (crime_name in did_crime_names){
    dftemp2 <- read_csv(paste("../Data/Processed/did_year_", crime_name, "_1994_2016_", data_source, ".csv",sep=""), show_col_types = FALSE)
    dftemp <- cbind(dftemp, dftemp2)
  }
  return(dftemp)
}
```

### did_latex
```{r}
did_latex <- function(did_combd,tbl_title = NULL,data_source){
  # change the name of the columns
  names(did_combd) <- c('Total Crime', 'Murder', 'Rape', 'Robbery', 'Assault', 'Aggravated Assault', 'Burglary', 'Theft')
  # change the names of the rows
  rownames(did_combd) <- c("Mean", "SE")
  # make the table
  print(xtable(did_combd, digits = c(2, 2, 2, 2, 2, 2, 2, 2, 2),caption = tbl_title), caption.placement='top', file=paste("../Tables/did_", data_source, ".txt", sep=""))
}
```

-------
FBI UCR
-------
### Data cleaning
```{r}
# this section loads the data, removes data from DC, removes reporting agencies that have high discrepancy, and removes reporting agencies that don't report consistently
df_n <- data_cleaning("es_1994-2016", TRUE) 
```

### Total crime (national data, no covariates)
```{r}
df_n <- replace_neg(df_n, actual_all_crimes)
# event study for each group for each time period 
out <- att_gt(yname = "actual_all_crimes", 
              tname = "year",
              idname = "ori9_factors",
              gname = "nibrs_year",
              xformla = ~1, # no covariates
              data = df_n,
              clustervars = c("ori9_factors", "state_fac"),
              est_method = "dr",
              control_group = "notyettreated",
              base_period = "universal"
              )
# the following function saves the figure and prints a latex table as well
# it outputs a figure
pc <- post_processing(data_type="n",crime_abbr="c",crime_name="crime",title="Event study of total crime (FBI UCR)",freq="annual",alt=FALSE)
```

### Murder
```{r}
df_n <- replace_neg(df_n, actual_murder)
# event study for each group for each time period 
out <- att_gt(yname = "actual_murder", 
              tname = "year",
              idname = "ori9_factors",
              gname = "nibrs_year",
              xformla = ~1, # no covariates
              data = df_n,
              clustervars = c("ori9_factors", "state_fac"),
              est_method = "dr",
              control_group = "notyettreated",
              base_period = "universal"
              )
# the following function saves the figure and prints a latex table as well
pm <- post_processing(data_type="n",crime_abbr="m",crime_name="murder",title="Event study of murder (FBI UCR)",freq="annual",alt=FALSE)
```

### Rape
```{r}
df_n <- replace_neg(df_n, actual_rape_total)
# event study for each group for each time period 
out <- att_gt(yname = "actual_rape_total", 
              tname = "year",
              idname = "ori9_factors",
              gname = "nibrs_year",
              xformla = ~1, # no covariates
              data = df_n,
              clustervars = c("ori9_factors", "state_fac"),
              est_method = "dr",
              control_group = "notyettreated",
              base_period = "universal"
              )
# the following function saves the figure and prints a latex table as well
prp <- post_processing(data_type="n",crime_abbr="p",crime_name="rape",title="Event study of rape (FBI UCR)",freq="annual",alt=FALSE)
```

### Robbery
```{r}
df_n <- replace_neg(df_n, actual_robbery_total)
# event study for each group for each time period 
out <- att_gt(yname = "actual_robbery_total", 
              tname = "year",
              idname = "ori9_factors",
              gname = "nibrs_year",
              xformla = ~1, # no covariates
              data = df_n,
              clustervars = c("ori9_factors", "state_fac"),
              est_method = "dr",
              control_group = "notyettreated",
              base_period = "universal"
              )
# the following function saves the figure and prints a latex table as well
pry <- post_processing(data_type="n",crime_abbr="r",crime_name="robbery",title="Event study of robbery (FBI UCR)",freq="annual",alt=FALSE)
```


### Assault
```{r}
df_n <- replace_neg(df_n, actual_assault_total)
# did for assault
didreg_a = lm(actual_assault_total ~ nibrs + year + did, data=df_n)
summary(didreg_a)
# event study for each group for each time period 
out <- att_gt(yname = "actual_assault_total", 
              tname = "year",
              idname = "ori9_factors",
              gname = "nibrs_year",
              xformla = ~1, # no covariates
              data = df_n,
              clustervars = c("ori9_factors", "state_fac"),
              est_method = "dr",
              control_group = "notyettreated",
              base_period = "universal"
              )
# the following function saves the figure and prints a latex table as well
pa <- post_processing(data_type="n",crime_abbr="a",crime_name="assault",title="Event study of assault (FBI UCR)",freq="annual",alt=FALSE)
```


### Aggravated Assault
```{r}
df_n <- replace_neg(df_n, actual_assault_aggravated)
# event study for each group for each time period 
out <- att_gt(yname = "actual_assault_aggravated", 
              tname = "year",
              idname = "ori9_factors",
              gname = "nibrs_year",
              xformla = ~1, # no covariates
              data = df_n,
              clustervars = c("ori9_factors", "state_fac"),
              est_method = "dr",
              control_group = "notyettreated",
              base_period = "universal"
              )
# the following function saves the figure and prints a latex table as well
paa <- post_processing(data_type="n",crime_abbr="aa",crime_name="agg_assault",title="Event study of aggravated assault (FBI UCR)",freq="annual",alt=FALSE)
```


### Burglary
```{r}
df_n <- replace_neg(df_n, actual_burg_total)
# event study for each group for each time period 
out <- att_gt(yname = "actual_burg_total", 
              tname = "year",
              idname = "ori9_factors",
              gname = "nibrs_year",
              xformla = ~1, # no covariates
              data = df_n,
              clustervars = c("ori9_factors", "state_fac"),
              est_method = "dr",
              control_group = "notyettreated",
              base_period = "universal"
              )
# the following function saves the figure and prints a latex table as well
pb <- post_processing(data_type="n",crime_abbr="b",crime_name="burglary",title="Event study of burglary (FBI UCR)",freq="annual",alt=FALSE)
```


### Theft
```{r}
df_n <- replace_neg(df_n, actual_theft_total)
# event study for each group for each time period 
out <- att_gt(yname = "actual_theft_total", 
              tname = "year",
              idname = "ori9_factors",
              gname = "nibrs_year",
              xformla = ~1, # no covariates
              data = df_n,
              clustervars = c("ori9_factors", "state_fac"),
              est_method = "dr",
              control_group = "notyettreated",
              base_period = "universal"
              )
# the following function saves the figure and prints a latex table as well
pt <- post_processing(data_type="n",crime_abbr="t",crime_name="theft",title="Event study of theft (FBI UCR)",freq="annual",alt=FALSE)
```

### --DiD--
Combine did results
```{r}
did_combd <- did_comb(data_source = "n")
```


Make LaTeX table
```{r}
did_latex(did_combd = did_combd, data_source = "n")
```


-------
Alt UCR
-------
### Data cleaning
```{r}
df_na <- data_cleaning("es_1994-2016_robust_exp", TRUE)
```

### Total crime (national data, SRS substitution, no covariates)
```{r}
# replace negative values
df_na <- replace_neg(df_na,actual_all_crimes)
# event study for each group for each time period
out <- att_gt(yname = "actual_all_crimes", 
              tname = "year",
              idname = "ori9_factors",
              gname = "nibrs_year",
              xformla = ~1,
              data = df_na,
              clustervars = c("ori9_factors", "state_fac"), 
              control_group = "notyettreated",
              base_period = "universal",
              est_method = "dr"
              )
# the following function saves the figure and saves a latex table as well
pc_a <- post_processing(data_type="na",crime_abbr="c",crime_name="crime",title="Event study of total crime (Alternative UCR)",freq="annual",alt=TRUE)
```

### Murder
```{r}
# 9 of the values for actual_murder are negative. I replaced them with the average value for the agency
df_na <- replace_neg(df_na,actual_murder)
# event study for each group for each time period 
out <- att_gt(yname = "actual_murder", 
              tname = "year",
              idname = "ori9_factors",
              gname = "nibrs_year",
              xformla = ~1, # no covariates
              data = df_na,
              clustervars = c("ori9_factors", "state_fac"),
              est_method = "dr",
              control_group = "notyettreated",
              base_period = "universal"
              )
# the following function saves the figure and prints a latex table as well
pm_a <- post_processing(data_type="na",crime_abbr="m",crime_name="murder",title="Event study of murder (Alternative UCR)",freq="annual",alt=TRUE)
```


### Rape
```{r}
# replace negative values
df_na <- replace_neg(df_na,actual_rape_total)
# event study for each group for each time period 
out <- att_gt(yname = "actual_rape_total", 
              tname = "year",
              idname = "ori9_factors",
              gname = "nibrs_year",
              xformla = ~1, # no covariates
              data = df_na,
              clustervars = c("ori9_factors", "state_fac"),
              est_method = "dr",
              control_group = "notyettreated",
              base_period = "universal"
              )
# the following function saves the figure and prints a latex table as well
prp_a <- post_processing(data_type="na",crime_abbr="p",crime_name="rape",title="Event study of rape (Alternative UCR)",freq="annual",alt=TRUE)
```


### Robbery
```{r}
df_na <- replace_neg(df_na,actual_robbery_total)
# event study for each group for each time period 
out <- att_gt(yname = "actual_robbery_total", 
              tname = "year",
              idname = "ori9_factors",
              gname = "nibrs_year",
              xformla = ~1, # no covariates
              data = df_na,
              clustervars = c("ori9_factors", "state_fac"),
              est_method = "dr",
              control_group = "notyettreated",
              base_period = "universal"
              )
# the following function saves the figure and prints a latex table as well
pry_a <- post_processing(data_type="na",crime_abbr="r",crime_name="robbery",title="Event study of robbery (Alternative UCR)",freq="annual",alt=TRUE)
```


### Assault
```{r}
df_na <- replace_neg(df_na,actual_assault_total)
# event study for each group for each time period 
out <- att_gt(yname = "actual_assault_total", 
              tname = "year",
              idname = "ori9_factors",
              gname = "nibrs_year",
              xformla = ~1, # no covariates
              data = df_na,
              clustervars = c("ori9_factors", "state_fac"),
              est_method = "dr",
              control_group = "notyettreated",
              base_period = "universal"
              )
# the following function saves the figure and prints a latex table as well
pa_a <- post_processing(data_type="na",crime_abbr="a",crime_name="assault",title="Event study of assault (Alternative UCR)",freq="annual",alt=TRUE)
```


### Aggravated Assault
```{r}
df_na <- replace_neg(df_na,actual_assault_aggravated)
# event study for each group for each time period 
out <- att_gt(yname = "actual_assault_aggravated", 
              tname = "year",
              idname = "ori9_factors",
              gname = "nibrs_year",
              xformla = ~1, # no covariates
              data = df_na,
              clustervars = c("ori9_factors", "state_fac"),
              est_method = "dr",
              control_group = "notyettreated",
              base_period = "universal"
              )
# the following function saves the figure and prints a latex table as well
paa_a <- post_processing(data_type="na",crime_abbr="aa",crime_name="agg_assault",title="Event study of agg. assault (Alternative UCR)",freq="annual",alt=TRUE)
```


### Burglary
```{r}
df_na <- replace_neg(df_na,actual_burg_total)
# event study for each group for each time period 
out <- att_gt(yname = "actual_burg_total", 
              tname = "year",
              idname = "ori9_factors",
              gname = "nibrs_year",
              xformla = ~1, # no covariates
              data = df_na,
              clustervars = c("ori9_factors", "state_fac"),
              est_method = "dr",
              control_group = "notyettreated",
              base_period = "universal"
              )
# the following function saves the figure and prints a latex table as well
pb_a <- post_processing(data_type="na",crime_abbr="b",crime_name="burglary",title="Event study of burglary (Alternative UCR)",freq="annual",alt=TRUE)
```


### Theft
```{r}
df_na <- replace_neg(df_na,actual_theft_total)
# event study for each group for each time period 
out <- att_gt(yname = "actual_theft_total", 
              tname = "year",
              idname = "ori9_factors",
              gname = "nibrs_year",
              xformla = ~1, # no covariates
              data = df_na,
              clustervars = c("ori9_factors", "state_fac"),
              est_method = "dr",
              control_group = "notyettreated",
              base_period = "universal"
              )
# the following function saves the figure and prints a latex table as well
pt_a <- post_processing(data_type="na",crime_abbr="t",crime_name="theft",title="Event study of theft (Alternative UCR)",freq="annual",alt=TRUE)
```



### --DiD--
Combine did results
```{r}
did_combd <- did_comb(data_source = "na")
```


Make LaTeX table
```{r}
did_latex(did_combd = did_combd, data_source = "na")
```


## Graphing
### get_legend
```{r}
mytheme <- theme(plot.title = element_text(size=8),
            axis.title.x=element_text(size=8),
            axis.title.y=element_text(size=8),
            axis.text = element_text(size=8),
            legend.position="none")
mylabels <- labs(caption=NULL)
get_legend<-function(myggplot){
    tmp <- ggplot_gtable(ggplot_build(myggplot))
    leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
    legend <- tmp$grobs[[leg]]
    return(legend)
}
mylegend <- g_legend(pc)
myytitle <- pc$labels$y
myxtitle <- pc$labels$x
mycaption <- pc$labels$caption
```


### Total crime
```{r,fig.height=3, fig.width=7}
# reduce spaces around the plot
mytheme <- gridExtra::ttheme_default(
             core = list(padding=unit(c(1, 1), "mm"))
           )
pc_pca <- grid.arrange(
  arrangeGrob(pc+mytheme+mylabels,top="(a)"), 
  arrangeGrob(pca+mytheme+mylabels,top="(b)"),
  bottom=mylegend$grobs[[1]],ncol=2
  )
ggsave("../Figures/pc_pca.jpg", pc_pca, height = unit(3, "in"))
```


### Crime categories
```{r, fig.height=9.5, fig.width=7}
# murder, rape, robbery, assault
p_p_a_1 <- grid.arrange(
  arrangeGrob(pm+mytheme+mylabels, prp+mytheme+mylabels, pry+mytheme+mylabels, 
              pa+mytheme+mylabels, top="(a)",ncol=1), 
  arrangeGrob(pm_a+mytheme+mylabels, prp_a+mytheme+mylabels, pry_a+mytheme+mylabels, 
              pa_a+mytheme+mylabels, top="(b)",ncol=1),
  mylegend,
  nrow=2, layout_matrix=rbind(c(1,2),c(3,3)), heights=c(9,.5))
ggsave("../Figures/p_p_a_1.jpg", p_p_a_1, width = unit(7, "in"), height = unit(9.5, "in"))
```

```{r, fig.height=7.5, fig.width=7}
# aggravated assault, burglary, theft
p_p_a_2 <- grid.arrange(
  arrangeGrob(paa+mytheme+mylabels, pb+mytheme+mylabels, pt+mytheme+mylabels, 
              top="(a)",ncol=1), 
  arrangeGrob(paa_a+mytheme+mylabels, pb_a+mytheme+mylabels, pt_a+mytheme+mylabels, 
              top="(b)",ncol=1),
  mylegend, layout_matrix=rbind(c(1,2),c(3,3)), nrow=2, heights=c(7,.5))
ggsave("../Figures/p_p_a_2.jpg", p_p_a_2, width = unit(7, "in"), height = unit(7.5, "in"))
```


## Detach all libraries
pacman::p_unload(pacman::p_loaded(), character.only = TRUE)